\papertitle

### 2014-03-16 final-report/paper.tex
Better

We propose a visualization system for understanding and exploring query execution and data movement in a distributed database system. Our tool will provide insight into: (1) data flow between query fragments and between workers, (2) query execution and operator dependencies, (3) cluster utilization, (4) network utilization. Our tool will help developers understand and improve query execution, and will provide insight into common problems such as data skew or performance bottlenecks.

In particular, our visualization system is built to inspect query execution in Myria\footnote{\url{http://myria.cs.washington.edu/}}, a distributed big data management system currently being developed in the UW CSE database group. Myria aims towards building a distributed database platform to provide \emph{big data management and analytics as a service} primarily for scientific applications.

Our vision is to build a generic visualization that can be used for other systems as well (e.g. Spark, Hadoop). This project builds on an existing prototype that uses logs generated during query execution to create a time series visualization of operator states.

@@

Dapper and X-trace focus on how data flows through a distributed system. In \system the visualization focuses on the operators and how the data flows through them. This orthogonal view is better suited for debugging performance bottlenecks in distributed DBMS and also scales to a larger number of events. Furthermore, in contrast to  we offer different abstraction levels, which enables users to find problems faster and handle larger amounts of profiling data. Also, \system is specifically designed to help developers understand query execution in distributed database system like Myria as opposed to general traces in distributed systems.

@@

\system is awesome.

>>>>

We propose a visualization system for understanding and exploring query execution and data movement in a distributed database management system (DDBMS). Our tool will provide insight into: (1) data flow between query fragments and between workers, (2) query execution and operator dependencies, (3) cluster utilization, (4) network utilization. Our tool, which we call \system, will help developers understand and improve query execution, and will provide insight into common problems such as data skew or performance bottlenecks.

In particular, \system is built to inspect query execution in Myria\footnote{\url{http://myria.cs.washington.edu/}}, a distributed big data management system currently being developed in the UW CSE database group. Myria aims towards building a distributed database platform to provide \emph{big data management and analytics as a service} primarily for scientific applications.

The proposed visualizations can easily be applied to other DDBMS as well (e.g. Spark, Hadoop).

@@

Dapper and X-trace focus on how data flows through a distributed system. In \system the visualization focuses on the operators and how the data flows through them. This orthogonal view is better suited for debugging performance bottlenecks in DDBMS and also scales to a larger number of events. Furthermore, in contrast to  we offer different abstraction levels, which enables users to find problems faster and handle larger amounts of profiling data. Also, \system is specifically designed to help developers understand query execution in distributed database system like Myria as opposed to general traces in distributed systems.

@@
